Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse

### 2014-12-18 Results.tex
More comments

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, even with substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

@@

Introducing information sharing amongst women leads the behaviour of the decision rules to diverge markedly. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions. Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because information sharing exacerbates the existing tendency to pool with moderate drinkers, who behave more honestly as heavy drinkers become less so.

Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the .25 level, and the associated increase in false positives. This arises because of the lack of homophilly in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal. The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.

The relationship is not, however, entirely straighforward, in that increasing information sharing leads to greater variance between runs. A linear model was was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis.

@@

For the median signal choice of moderate drinkers, the emulator results suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively. For the Lexicographic rule, the overwhelming majority of variance in signalling behaviour is attributable to the proportions of midwives (44\% \(p_{m}(m)\), 7\% \(p_{l}(m)\), and a further 15\% for their interaction).  The proportions of midwives are also key drivers in group separation, and the between run IQR of both measures for this rule.

>>>>

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, even with substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

@@

Introducing information sharing amongst women leads the behaviour of the decision rules to diverge markedly. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions. Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because information sharing exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.

Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), and the associated increase in false positives. This arises because of the lack of homophilly in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal. The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.

The relationship is not, however, entirely straighforward, in that increasing information sharing leads to greater variance between runs. A linear model was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.

@@

For the median signal choice of moderate drinkers, the results of the sensitivity analysis suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively. For the Lexicographic rule, the overwhelming majority of variance in signalling behaviour is reflective of the prevalence of stigmatisation by midwives (44\% \(p_{m}(m)\), 7\% \(p_{l}(m)\), and a further 15\% for their interaction).  The proportions of midwives are also key drivers in group separation, and the between run IQR of both measures for this rule.
